Student Log-Data from a Randomized Evaluation of Educational Technology: A Causal Case Study

### 2020-05-13 paper.Rnw
revised statements of applied conclusions #2

The last two columns of Table \ref{tab:matchResults} give sensitivity intervals for each of the three weighted average treatment effects.
The column of Table \ref{tab:matchResults} labeled ``[Pretest]''
accounts for the possible omission of a covariate $U$ that, at most, predicts $Y$ and $H$ as well as do pretest scores.
The resulting sensitivity intervals are quite wide, including
both large negative effects as well as substantial positive
effects.
In fact, pretest is the most important of our observed covariates; it is the observed covariate whose omission would cause the most bias.
This is unsurprising, since pretests are generally considered to be the most important covariate to measure, and studies that include pretest measures often reproduce experimental estimates \citep[e.g.][]{cook2008three,cook2009bias}.
Therefore, a sensitivity analysis considering an omitted covariate as important as pretest scores may be too pessimistic.
Instead,
the final column of Table \ref{tab:matchResults} gives sensitivity intervals for the omission of a covariate that, at most, predicts $Y$ and $H$ as well as ethnicity dummy variables, the second most important of our observed covariates.
These sensitivity intervals are also wide, but the interval corresponding
to OLS weights is entirely negative.

The conclusion is that the omission of a confounder as important as ethnicity indicators
cannot explain the estimated OLS-weighted ATE.
Allowing for the possible omission of such a covariate, we infer that requesting a
large number of hints hurts students' posttest scores.
The size of the effect may be as small as
\Sexpr{min(abs(round(sens[['prec_eff']]['race',]*100)))}\% of a standard deviation
or as large as \Sexpr{max(abs(round(sens[['prec_eff']]['race',]*100)))}\% of a standard deviation.

@@

$\hat{\Delta}$ estimates the difference between the average outcome
for students in the entire treatment group, and the average outcome
for the treatment group were $H=0$ for all students.
That is
\begin{equation*}
\Delta=\EE[Y(1,H(1))-Y(1,0)|Z=1]
\end{equation*}
This can be re-written:
\begin{align*}
\begin{split}
\Delta&=\EE[Y(1,1)-Y(1,0)|Z=1,H=1]Pr(H=1)\\
&\qquad +\EE[Y(1,0)-Y(1,0)|Z=1,H=0]Pr(H=0)
\end{split}
\\[2ex]
&=\EE[Y(1,1)-Y(1,0)|Z=1,H=1]Pr(H=1)\\
&=Pr(H=1)TOT
\end{align*}
Since $Pr(H=1)=$\Sexpr{round(mixProp,2)} by definition,
$\hat{\Delta}=$\Sexpr{round(mixProp,2)}$TOT$.
Estimated thusly, the indirect effect is negative: \Sexpr{round(effects[['tot_eff']][['coefficients']]*(mixProp),2)}, with
a standard error of \Sexpr{round(effects$tot_eff$std.error*(mixProp),2)}.
This analysis suggests that the availability of hints
actually \emph{lowers} the treatment effect, that CTA1 works not
because of hints, but despite them.

@@

Table \ref{tab:mediation} summarizes our mediation results.

@@

Our observational study suggested that hint requests have a negative effect: students who
requested hints more often than the \Sexpr{round((1-mixProp)*100)}th
percentile score lower on the posttest, after controlling for observed
covariates.
As far as we can tell, the optimal strategy is to request few, if any, hints.
While our estimate is subject to bias from an omitted confounder, the omitted variable must be a relatively strong predictor of hint usage and of posttest scores in order to explain the observed relationship.
An omitted confounder that is as important as pretest could explain the relationship, but an omitted confounder as important as ethnicity---our second most important covariate---could not (so long as we estimate an OLS-weighted average effect).

Mediation analysis essentially interprets the observational study result in terms of the
overall CTA1 treatment effect.
Specifically, our analysis showed that CTA1 affected students'
posttest scores in (at least) two opposite ways: by allowing hints, it
lowered their posttest scores, but its other mechanisms increased
their scores by an even greater amount.

>>>>

The last two columns of Table \ref{tab:matchResults} give sensitivity intervals for each of the three weighted average treatment effects.
The column of Table \ref{tab:matchResults} labeled ``[Pretest]''
accounts for the possible omission of a covariate $U$ that, at most, predicts $Y$ and $H$ as well as do pretest scores.
The resulting sensitivity intervals are quite wide, including
both large negative effects as well as substantial positive
effects.
In fact, pretest is the most important of our observed covariates; it is the observed covariate whose omission would cause the most bias.
This is unsurprising, since pretests are generally considered to be the most important covariate to measure, and studies that include pretest measures often reproduce experimental estimates \citep[e.g.][]{cook2008three,cook2009bias}.
Therefore, a sensitivity analysis considering an omitted covariate as important as pretest scores may be too pessimistic.
On the other hand, it is likely that pretest scores do not fully capture between-student variance in academic ability; that is, there may be important components of prior ability (such as the ability to learn algebra) that are correlated with hint requests and posttest scores but not reflected in pretest scores.
A hypothetical measurement of one of those components may indeed have constituted a more important covariate than pretest scores.

A more optimistic scenario is reflected in the final column of Table \ref{tab:matchResults}.
That column gives sensitivity intervals for the omission of a covariate that, at most, predicts $Y$ and $H$ as well as ethnicity dummy variables, the second most important of our observed covariates.
These sensitivity intervals are also wide, but the interval corresponding
to OLS weights is entirely negative.

The conclusion is that the omission of a confounder as important as ethnicity indicators
cannot explain the estimated OLS-weighted ATE.
Allowing for the possible omission of such a covariate, the results suggest that requesting a
large number of hints hurts students' posttest scores.
The size of the effect may be as small as
\Sexpr{min(abs(round(sens[['prec_eff']]['race',]*100)))}\% of a standard deviation
or as large as \Sexpr{max(abs(round(sens[['prec_eff']]['race',]*100)))}\% of a standard deviation.

@@

$\hat{\Delta}$ estimates the difference between the average outcome
for students in the entire treatment group, and the average outcome
for the treatment group were $H=0$ for all students.
That is
\begin{equation*}
\Delta=\EE[Y(1,H(1))-Y(1,0)|Z=1]
\end{equation*}
This can be re-written:
\begin{align*}
\begin{split}
\Delta&=\EE[Y(1,1)-Y(1,0)|Z=1,H=1]Pr(H=1)\\
&\qquad +\EE[Y(1,0)-Y(1,0)|Z=1,H=0]Pr(H=0)
\end{split}
\\[2ex]
&=\EE[Y(1,1)-Y(1,0)|Z=1,H=1]Pr(H=1)\\
&=Pr(H=1)TOT
\end{align*}
Since $Pr(H=1)=$\Sexpr{round(mixProp,2)} by definition,
$\hat{\Delta}=$\Sexpr{round(mixProp,2)}$TOT$.
Estimated thusly, the indirect effect is negative: \Sexpr{round(effects[['tot_eff']][['coefficients']]*(mixProp),2)}, with
a standard error of \Sexpr{round(effects$tot_eff$std.error*(mixProp),2)}.
Like the $TOT$ estimate on which it is based, this estimate of indirect effects assumes matched ignorabilty---no confounding between $H$ and $Y$ within matched sets.
With this important caveat, this analysis suggests that the availability of hints
actually \emph{lowers} the treatment effect, that CTA1 works not
because of hints, but despite them.

@@

Table \ref{tab:mediation} summarizes our mediation results: assuming matched ignorability, assignment to CTA1 increases student test scores despite the availablity of hints (an indirect effect of \Sexpr{round(mixProp*effects[['tot_eff']][['coefficients']],2)} standard deviations), and the effect due to CTA1's other mechanisms is \Sexpr{round(dir2.1t[1],2)}.

@@

Our observational study suggested that hint requests have a negative effect: students who
requested hints more often than the \Sexpr{round((1-mixProp)*100)}th
percentile score lower on the posttest, after controlling for observed
covariates.
Taken at face value, this suggests that the optimal strategy is to request few, if any, hints.
%While our estimate is subject to bias from an omitted confounder, the omitted variable must be a relatively strong predictor of hint usage and of posttest scores in order to explain the observed relationship.
However, this conclusion assumes that there were no omitted confounders.
An omitted confounder that is as important as pretest could explain the relationship, but an omitted confounder as important as ethnicity---our second most important covariate---could not (so long as we estimate an OLS-weighted average effect).

Mediation analysis essentially interprets the observational study result in terms of the
overall CTA1 treatment effect.
Specifically, the analysis in \ref{sec:mediation} showed that CTA1 affected students'
posttest scores in (at least) two opposite ways: by allowing hints, it
lowered their posttest scores, but its other mechanisms increased
their scores by an even greater amount.

### 2020-05-13 paper.tex
revised statements of applied conclusions #2

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Fri May  8 16:01:57 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllccc}
  \hline
  &&&&\multicolumn{2}{c}{Sensitivity Intervals}\\
 Weights&Estimate&Std. Error&CI&[Pretest]&[Ethnicity] \\
 \hline
OLS & -0.18 & 0.04 & [-0.25,-0.10] & [-0.41,0.06] & [-0.30,-0.05] \\ 
  ATE & -0.12 & 0.05 & [-0.23,-0.02] & [-0.45,0.20] & [-0.29,0.04] \\ 
  TOT & -0.14 & 0.06 & [-0.25,-0.03] & [-0.47,0.19] & [-0.31,0.03] \\ 
   \hline
\end{tabular}
\caption{Estimates, standard errors, and sensitivity analysis of the weighted average effect of hint usage on posttest scores, under different weighting schemes.} 
\label{tab:matchResults}
\end{table}

@@

The last two columns of Table \ref{tab:matchResults} give sensitivity intervals for each of the three weighted average treatment effects.
The column of Table \ref{tab:matchResults} labeled ``[Pretest]''
accounts for the possible omission of a covariate $U$ that, at most, predicts $Y$ and $H$ as well as do pretest scores.
The resulting sensitivity intervals are quite wide, including
both large negative effects as well as substantial positive
effects.
In fact, pretest is the most important of our observed covariates; it is the observed covariate whose omission would cause the most bias.
This is unsurprising, since pretests are generally considered to be the most important covariate to measure, and studies that include pretest measures often reproduce experimental estimates \citep[e.g.][]{cook2008three,cook2009bias}.
Therefore, a sensitivity analysis considering an omitted covariate as important as pretest scores may be too pessimistic.
Instead,
the final column of Table \ref{tab:matchResults} gives sensitivity intervals for the omission of a covariate that, at most, predicts $Y$ and $H$ as well as ethnicity dummy variables, the second most important of our observed covariates.
These sensitivity intervals are also wide, but the interval corresponding
to OLS weights is entirely negative.

The conclusion is that the omission of a confounder as important as ethnicity indicators
cannot explain the estimated OLS-weighted ATE.
Allowing for the possible omission of such a covariate, we infer that requesting a
large number of hints hurts students' posttest scores.
The size of the effect may be as small as
5\% of a standard deviation
or as large as 30\% of a standard deviation.

@@

$\hat{\Delta}$ estimates the difference between the average outcome
for students in the entire treatment group, and the average outcome
for the treatment group were $H=0$ for all students.
That is
\begin{equation*}
\Delta=\EE[Y(1,H(1))-Y(1,0)|Z=1]
\end{equation*}
This can be re-written:
\begin{align*}
\begin{split}
\Delta&=\EE[Y(1,1)-Y(1,0)|Z=1,H=1]Pr(H=1)\\
&\qquad +\EE[Y(1,0)-Y(1,0)|Z=1,H=0]Pr(H=0)
\end{split}
\\[2ex]
&=\EE[Y(1,1)-Y(1,0)|Z=1,H=1]Pr(H=1)\\
&=Pr(H=1)TOT
\end{align*}
Since $Pr(H=1)=$0.3 by definition,
$\hat{\Delta}=$0.3$TOT$.
Estimated thusly, the indirect effect is negative: -0.04, with
a standard error of 0.02.
This analysis suggests that the availability of hints
actually \emph{lowers} the treatment effect, that CTA1 works not
because of hints, but despite them.

@@

Table \ref{tab:mediation} summarizes our mediation results.

@@

Our observational study suggested that hint requests have a negative effect: students who
requested hints more often than the 70th
percentile score lower on the posttest, after controlling for observed
covariates.
As far as we can tell, the optimal strategy is to request few, if any, hints.
While our estimate is subject to bias from an omitted confounder, the omitted variable must be a relatively strong predictor of hint usage and of posttest scores in order to explain the observed relationship.
An omitted confounder that is as important as pretest could explain the relationship, but an omitted confounder as important as ethnicity---our second most important covariate---could not (so long as we estimate an OLS-weighted average effect).

Mediation analysis essentially interprets the observational study result in terms of the
overall CTA1 treatment effect.
Specifically, our analysis showed that CTA1 affected students'
posttest scores in (at least) two opposite ways: by allowing hints, it
lowered their posttest scores, but its other mechanisms increased
their scores by an even greater amount.

@@

\subsection{Stan Code}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## data{
## //Sample sizes
##  int<lower=1> N; // total number of obs (long format)
##  int<lower=1> nstud; // # students
##  int<lower=1> nsec; // # sections (problems nested in sections)
## 
## // indices
##  int<lower=1,upper=nstud> studentM[N]; //for each obs, which student?
##  int<lower=1,upper=nsec> section[N]; // for each obs, which section?
## 
## // data data
##  int<lower=0,upper=1> hint[N]; // for each obs, was a hint requested?
## 
## }
## parameters{
## 
##  vector[nstud] eta; // ability parameter
##  real<lower=0,upper=1> p1; // mixing proportion
##  //ordered[2] mu;             // locations of mixture components
##  real<upper=0> mu0; //location of mixture component 0
##  vector<lower=0>[2] sigma;  // scales of mixture components
## 
##  real delta[nsec]; // section difficulty parameter
##  //real<lower=0> sigSec; // scale of difficulty parameters
## 
## }
## transformed parameters{
##  real<lower=0> mu1; // location of mixture component 1
##  mu1= -(1-p1)/p1*mu0;
## }
## model{
##  // logs of mixing proportions to save time
##  real log_p1=log(p1);
##  real log_p0=log(1-p1);
## 
## // linear predictor for logit model
##  real linPred[N];
## 
## // priors
##  sigma ~ lognormal(0, 2);
##  mu0 ~ normal(0, 2);
## // sigSec ~ lognormal(0,2);
##  p1~ beta(2,2); // I'd rather the groups have similar sizes
## 
## // model for section difficulty parameters
##  delta~normal(0,3);//sigSec);
## 
## // Rasch model for hint requests
##  for(i in 1:N)
##   linPred[i]= eta[studentM[i]]-delta[section[i]];
## 
##  hint~bernoulli_logit(linPred);
## 
## 
## // mixture model for ability parameters
##  for(n in 1:nstud)
##   target += log_sum_exp(log_p0+normal_lpdf(eta[n]|mu0,sigma[1]),
## 			log_p1+normal_lpdf(eta[n]|mu1,sigma[2]));
## 
## }
\end{verbatim}
\end{kframe}
\end{knitrout}
%\clearpage
\section{Covariate Balance Before and After Matching}
% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Fri May  8 16:01:58 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  &\multicolumn{3}{c}{Unmatched}&\multicolumn{3}{c}{Matched}\\
 \hline
 & std.diff & z &  & std.diff & z &  \\ 
  \hline
grade9 & -0.34 & -7.05 & *** & 0.03 & 0.44 &     \\ 
  gradehigher & 0.34 & 7.05 & *** & -0.03 & -0.44 &     \\ 
  raceWhiteAsian & -0.64 & -12.83 & *** & 0.03 & 0.75 &     \\ 
  raceBlackMulti & 0.23 & 4.71 & *** & 0.01 & 0.24 &     \\ 
  raceHispAIAN & 0.51 & 10.35 & *** & -0.05 & -0.98 &     \\ 
  xirt & -0.52 & -10.54 & *** & 0.09 & 1.82 & .   \\ 
  spectypical & -0.16 & -3.32 & *** & 0.03 & 0.48 &     \\ 
  specspeced & 0.34 & 7.07 & *** & -0.10 & -1.44 &     \\ 
  specgifted & -0.14 & -3.03 & **  & 0.06 & 1.16 &     \\ 
  esl0 & -0.37 & -7.70 & *** & 0.04 & 0.63 &     \\ 
  esl1 & 0.37 & 7.70 & *** & -0.04 & -0.63 &     \\ 
  stateCT & 0.58 & 11.81 & *** & -0.00 & 0.00 &     \\ 
  stateKY & -0.36 & -7.51 & *** & -0.00 & 0.00 &     \\ 
  stateLA & -0.08 & -1.68 & .   & -0.00 & 0.00 &     \\ 
  stateMI & -0.36 & -7.51 & *** & 0.00 & 0.00 &     \\ 
  stateTX & 0.43 & 8.77 & *** & 0.00 & 0.00 &     \\ 
   \hline
\end{tabular}
\caption{Covariate balance (standardized differences and Z-scores) before and after the propensity score match.} 
\label{tab:balance}
\end{table}

>>>>

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed May 13 17:14:14 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllccc}
  \hline
  &&&&\multicolumn{2}{c}{Sensitivity Intervals}\\
 Weights&Estimate&Std. Error&CI&[Pretest]&[Ethnicity] \\
 \hline
OLS & -0.18 & 0.04 & [-0.25,-0.10] & [-0.41,0.06] & [-0.30,-0.05] \\ 
  ATE & -0.12 & 0.05 & [-0.23,-0.02] & [-0.45,0.20] & [-0.29,0.04] \\ 
  TOT & -0.14 & 0.06 & [-0.25,-0.03] & [-0.47,0.19] & [-0.31,0.03] \\ 
   \hline
\end{tabular}
\caption{Estimates, standard errors, and sensitivity analysis of the weighted average effect of hint usage on posttest scores, under different weighting schemes.} 
\label{tab:matchResults}
\end{table}

@@

The last two columns of Table \ref{tab:matchResults} give sensitivity intervals for each of the three weighted average treatment effects.
The column of Table \ref{tab:matchResults} labeled ``[Pretest]''
accounts for the possible omission of a covariate $U$ that, at most, predicts $Y$ and $H$ as well as do pretest scores.
The resulting sensitivity intervals are quite wide, including
both large negative effects as well as substantial positive
effects.
In fact, pretest is the most important of our observed covariates; it is the observed covariate whose omission would cause the most bias.
This is unsurprising, since pretests are generally considered to be the most important covariate to measure, and studies that include pretest measures often reproduce experimental estimates \citep[e.g.][]{cook2008three,cook2009bias}.
Therefore, a sensitivity analysis considering an omitted covariate as important as pretest scores may be too pessimistic.
On the other hand, it is likely that pretest scores do not fully capture between-student variance in academic ability; that is, there may be important components of prior ability (such as the ability to learn algebra) that are correlated with hint requests and posttest scores but not reflected in pretest scores.
A hypothetical measurement of one of those components may indeed have constituted a more important covariate than pretest scores.

A more optimistic scenario is reflected in the final column of Table \ref{tab:matchResults}.
That column gives sensitivity intervals for the omission of a covariate that, at most, predicts $Y$ and $H$ as well as ethnicity dummy variables, the second most important of our observed covariates.
These sensitivity intervals are also wide, but the interval corresponding
to OLS weights is entirely negative.

The conclusion is that the omission of a confounder as important as ethnicity indicators
cannot explain the estimated OLS-weighted ATE.
Allowing for the possible omission of such a covariate, the results suggest that requesting a
large number of hints hurts students' posttest scores.
The size of the effect may be as small as
5\% of a standard deviation
or as large as 30\% of a standard deviation.

@@

$\hat{\Delta}$ estimates the difference between the average outcome
for students in the entire treatment group, and the average outcome
for the treatment group were $H=0$ for all students.
That is
\begin{equation*}
\Delta=\EE[Y(1,H(1))-Y(1,0)|Z=1]
\end{equation*}
This can be re-written:
\begin{align*}
\begin{split}
\Delta&=\EE[Y(1,1)-Y(1,0)|Z=1,H=1]Pr(H=1)\\
&\qquad +\EE[Y(1,0)-Y(1,0)|Z=1,H=0]Pr(H=0)
\end{split}
\\[2ex]
&=\EE[Y(1,1)-Y(1,0)|Z=1,H=1]Pr(H=1)\\
&=Pr(H=1)TOT
\end{align*}
Since $Pr(H=1)=$0.3 by definition,
$\hat{\Delta}=$0.3$TOT$.
Estimated thusly, the indirect effect is negative: -0.04, with
a standard error of 0.02.
Like the $TOT$ estimate on which it is based, this estimate of indirect effects assumes matched ignorabilty---no confounding between $H$ and $Y$ within matched sets.
With this important caveat, this analysis suggests that the availability of hints
actually \emph{lowers} the treatment effect, that CTA1 works not
because of hints, but despite them.

@@

Table \ref{tab:mediation} summarizes our mediation results: assuming matched ignorability, assignment to CTA1 increases student test scores despite the availablity of hints (an indirect effect of -0.04 standard deviations), and the effect due to CTA1's other mechanisms is 0.18.

@@

Our observational study suggested that hint requests have a negative effect: students who
requested hints more often than the 70th
percentile score lower on the posttest, after controlling for observed
covariates.
Taken at face value, this suggests that the optimal strategy is to request few, if any, hints.
%While our estimate is subject to bias from an omitted confounder, the omitted variable must be a relatively strong predictor of hint usage and of posttest scores in order to explain the observed relationship.
However, this conclusion assumes that there were no omitted confounders.
An omitted confounder that is as important as pretest could explain the relationship, but an omitted confounder as important as ethnicity---our second most important covariate---could not (so long as we estimate an OLS-weighted average effect).

Mediation analysis essentially interprets the observational study result in terms of the
overall CTA1 treatment effect.
Specifically, the analysis in \ref{sec:mediation} showed that CTA1 affected students'
posttest scores in (at least) two opposite ways: by allowing hints, it
lowered their posttest scores, but its other mechanisms increased
their scores by an even greater amount.

@@

\subsection{Stan Code}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## data{
## //Sample sizes
##  int<lower=1> N; // total number of obs (long format)
##  int<lower=1> nstud; // # students
##  int<lower=1> nsec; // # sections (problems nested in sections)
## 
## // indices
##  int<lower=1,upper=nstud> studentM[N]; //for each obs, which student?
##  int<lower=1,upper=nsec> section[N]; // for each obs, which section?
## 
## // data data
##  int<lower=0,upper=1> hint[N]; // for each obs, was a hint requested?
## 
## }
## parameters{
## 
##  vector[nstud] eta; // ability parameter
##  real<lower=0,upper=1> p1; // mixing proportion
##  //ordered[2] mu;             // locations of mixture components
##  real<upper=0> mu0; //location of mixture component 0
##  vector<lower=0>[2] sigma;  // scales of mixture components
## 
##  real delta[nsec]; // section difficulty parameter
##  //real<lower=0> sigSec; // scale of difficulty parameters
## 
## }
## transformed parameters{
##  real<lower=0> mu1; // location of mixture component 1
##  mu1= -(1-p1)/p1*mu0;
## }
## model{
##  // logs of mixing proportions to save time
##  real log_p1=log(p1);
##  real log_p0=log(1-p1);
## 
## // linear predictor for logit model
##  real linPred[N];
## 
## // priors
##  sigma ~ lognormal(0, 2);
##  mu0 ~ normal(0, 2);
## // sigSec ~ lognormal(0,2);
##  p1~ beta(2,2); // I'd rather the groups have similar sizes
## 
## // model for section difficulty parameters
##  delta~normal(0,3);//sigSec);
## 
## // Rasch model for hint requests
##  for(i in 1:N)
##   linPred[i]= eta[studentM[i]]-delta[section[i]];
## 
##  hint~bernoulli_logit(linPred);
## 
## 
## // mixture model for ability parameters
##  for(n in 1:nstud)
##   target += log_sum_exp(log_p0+normal_lpdf(eta[n]|mu0,sigma[1]),
## 			log_p1+normal_lpdf(eta[n]|mu1,sigma[2]));
## 
## }
\end{verbatim}
\end{kframe}
\end{knitrout}
%\clearpage
\section{Covariate Balance Before and After Matching}
% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed May 13 17:14:15 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  &\multicolumn{3}{c}{Unmatched}&\multicolumn{3}{c}{Matched}\\
 \hline
 & std.diff & z &  & std.diff & z &  \\ 
  \hline
grade9 & -0.34 & -7.05 & *** & 0.03 & 0.44 &     \\ 
  gradehigher & 0.34 & 7.05 & *** & -0.03 & -0.44 &     \\ 
  raceWhiteAsian & -0.64 & -12.83 & *** & 0.03 & 0.75 &     \\ 
  raceBlackMulti & 0.23 & 4.71 & *** & 0.01 & 0.24 &     \\ 
  raceHispAIAN & 0.51 & 10.35 & *** & -0.05 & -0.98 &     \\ 
  xirt & -0.52 & -10.54 & *** & 0.09 & 1.82 & .   \\ 
  spectypical & -0.16 & -3.32 & *** & 0.03 & 0.48 &     \\ 
  specspeced & 0.34 & 7.07 & *** & -0.10 & -1.44 &     \\ 
  specgifted & -0.14 & -3.03 & **  & 0.06 & 1.16 &     \\ 
  esl0 & -0.37 & -7.70 & *** & 0.04 & 0.63 &     \\ 
  esl1 & 0.37 & 7.70 & *** & -0.04 & -0.63 &     \\ 
  stateCT & 0.58 & 11.81 & *** & -0.00 & 0.00 &     \\ 
  stateKY & -0.36 & -7.51 & *** & -0.00 & 0.00 &     \\ 
  stateLA & -0.08 & -1.68 & .   & -0.00 & 0.00 &     \\ 
  stateMI & -0.36 & -7.51 & *** & 0.00 & 0.00 &     \\ 
  stateTX & 0.43 & 8.77 & *** & 0.00 & 0.00 &     \\ 
   \hline
\end{tabular}
\caption{Covariate balance (standardized differences and Z-scores) before and after the propensity score match.} 
\label{tab:balance}
\end{table}
